### 2018-07-05 paper/sphinxes.tex
Adds draft figure of OR-POR difference
Makes Sphinxes a subsection of the design section

\section{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer, in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.

\subsection{Overview of the Sphinx header format}

@@

\subsection{The Sphinxes extension for sets of nodes}

@@

>>>>

\subsection{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer, in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)

\begin{figure}
  \includegraphics[width=\linewidth]{figures/OR-POR.png}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference to traditional onion routing and 
    mixing.
  }
\end{figure}

\subsubsection{Overview of the Sphinx header format}

@@

\subsubsection{The Sphinxes extension for sets of nodes}

@@

\subsubsection{Sphinxes algorithms}
